Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-11 paper/main.tex
[issue 2.15] greater depth

The architecture of \cite{krizhevsky2012imagenet}
uses relatively large receptive fields ($11\times11$) in the first convolutional layers.
\citet{zeiler2014visualizing} and \cite{dieleman2015rotation}
also use large receptive fields of $7\times7$ and $6\times6$
in the first convolution layer, respectively.
However, we find that using a receptive field larger than $5\times5$ in the first
convolutional layer leads to worse performance.
This result is in agreement with \citet{simonyan2014very},
which features an extremely homogeneous architecture that only performs
$3\times3$ convolutions.
Using a large receptive field instead of a stack of multiple $3\times3$ convolutions
leads to a shallower network, and it is often preferable to increase
the depth by using smaller receptive fields.
However, we find that replacing the first layer with
a stack of two $3\times3$ convolutional layers increases the validation error,
but we still follow \citet{simonyan2014very} and add many
$3\times3$ convolutions (with zero-padding) in the remaining layers.

>>>>

The architecture of \cite{krizhevsky2012imagenet}
uses relatively large receptive fields ($11\times11$) in the first convolutional layers.
\citet{zeiler2014visualizing} and \cite{dieleman2015rotation}
also use large receptive fields of $7\times7$ and $6\times6$
in the first convolution layer, respectively.
However, we find that using a receptive field larger than $5\times5$ in the first
convolutional layer leads to worse performance.
This result is in agreement with
\changed{
the network of \citet{simonyan2014very}, which has become known as ``VGGNet".
}
VGGNet features an extremely homogeneous architecture that only performs
$3\times3$ convolutions.
Using a large receptive field instead of a stack of multiple $3\times3$ convolutions
leads to a shallower network, and it is often preferable to increase
the depth by using smaller receptive fields.
However, we find that replacing the first layer with
a stack of two $3\times3$ convolutional layers increases the validation error,
\changed{
and thus use a $5\times5$ convolution in the first layer.
}

\changed{
In the remaining layers, we still follow VGGNet and add many
$3\times3$ convolutions (with zero-padding of size 1 pixel).
Note that with the padding of 1 pixel for $3\times3$ convolutional layers,
the spatial resolution will be preserved after convolution.
Such preservation of spatial resolution allows us to build relatively deep
networks, as shown in Table~\ref{table:hyperparamters}.
The main contribution of VGGNet is in showing that the depth plays an important
role in good performance.
In our case, we start with four convolutional layers and progressively add more
layers, while monitoring the validation loss;
we stop at eight convolutoinal layers after we find that adding more layers
leads to worse performance.
We conjecture that a greater depth and hence larger number of parameters
lead to overfitting in our case.
}
